### 2017-10-13 Gruba/04-uc.tex

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers, categories and normalized vectors.
For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.

>>>>

As aforementioned, the clustering of K-Gru rests on the distance between vector samples, where the dimensions are combined with numbers(normalized to 0-1 range), categories and normalized vectors.
For simplicity, we shall first illustrate the distance calculation of the simple vectors with mono data type on each dimension and then demonstrate that of complex vectors in K-Gru.
